Appendix

### 2020-04-29 appendix/appendixV5.Rmd
Red coefs. Max Y-axis. Max size plots. Table 2. Regres tables.

@@

f1 <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(color = "black") +
  # Error Bars
  geom_errorbarh(height = 0.1) +
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels= function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="black", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank()) 
f1
ggsave("./plots/f1.png", width = 20, height = 10, units = "cm")

@@

f1b <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(color = "black") +
  # Error Bars
  geom_errorbarh(height = 0.1) +
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels= function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="black", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank())

@@

f2 <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(color = "black") +
  # Error Bars
  geom_errorbarh(height = 0.1) +
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels= function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="black", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank()) 
f2
ggsave("./plots/f2.png", width = 20, height = 10, units = "cm")
```

@@

f3 <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(color = "black") +
  # Error Bars
  geom_errorbarh(height = 0.1) +
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels= function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="black", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank())

f3
ggsave("./plots/f3.png", width = 20, height = 10, units = "cm")
```

@@

f4 <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(color = "black") +
  # Error Bars
  geom_errorbarh(height = 0.1) +
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels= function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="black", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank())

f4
ggsave("./plots/f4.png", width = 20, height = 10, units = "cm")
```

@@

f5 <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(color = "black") +
  # Error Bars
  geom_errorbarh(height = 0.1) +
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels= function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="black", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank())

f5
ggsave("./plots/f5.png", width = 20, height = 10, units = "cm")
```

@@

f6 <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(color = "black") +
  # Error Bars
  geom_errorbarh(height = 0.1) +
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels= function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="black", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank())

f6
ggsave("./plots/f6.png", width = 20, height = 10, units = "cm")
```

@@

f7 <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(color = "black") +
  # Error Bars
  geom_errorbarh(height = 0.1) +
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels= function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="black", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank())

f7
ggsave("./plots/f7.png", width = 20, height = 10, units = "cm")
```

@@

```{r, echo=FALSE, fig.width=12.5, fig.height=5}

blank = ggplot() + 
  geom_blank() +
  theme_minimal()
blank
ggsave("./plots/zz_blank.png", width = 20, height = 10, units = "cm")

plots = list.files(path = "./plots/", pattern = "*.png") %>%
  map(~{
    image_rotate(image_read(path = paste0("./plots/", .x)), 270)
  })

@@

f8 <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(color = "black") +
  # Error Bars
  geom_errorbarh(height = 0.1) +
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels= function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="black", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank())

f8
ggsave("./plots/f8.png", width = 20, height = 10, units = "cm")
```

@@

f8b <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(color = "black") +
  # Error Bars
  geom_errorbarh(height = 0.1) +
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels= function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="black", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank()) 
f8b
```

@@

```{r, echo=FALSE, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on percentage of public expenditure GDP (PCTGDP)",warning=FALSE}
mod2 <- tibble(
  TE = mod$TE,
  seTE = mod$seTE,
  studlab = mod$studlab,
  lower = mod$lower,
  upper = mod$upper,
  group = "A") %>%
  bind_rows(.,
            aux = tibble(
              TE = c(mod$TE.random, NA),
              seTE = c(mod$seTE.random, NA),
              studlab = c("Overall Effect", "Prediction Interval"),
              lower = c(mod$lower.random, mod$lower.predict),
              upper = c(mod$upper.random, mod$upper.predict),
              group = "B"))

f9 <- mod2 %>%
  ggplot(aes(y = reorder(studlab,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(color = "black") +
  # Error Bars
  geom_errorbarh(height = 0.1) +
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Vertical dashed line
  geom_vline(xintercept=0, color="black", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank()) 
f9
ggsave("./plots/f9.png", width = 20, height = 10, units = "cm")
```

@@

f10 <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(color = "black") +
  # Error Bars
  geom_errorbarh(height = 0.1) +
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels= function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="black", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank())

f10
ggsave("./plots/f10.png", width = 20, height = 10, units = "cm")
```

@@

f11 <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(color = "black") +
  # Error Bars
  geom_errorbarh(height = 0.1) +
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels= function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="black", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank())

f11
ggsave("./plots/f11.png", width = 20, height = 10, units = "cm")
```

@@

```{r, echo=FALSE, fig.width=10, fig.height=1}

@@

@@

>>>>

\newpage 
### Descriptive Stats of Moderators

```{r, echo=F}

#TABLE 2 ABOUT HERE: Moderator, frequency, percentage (mean and median for publication year)

aux = dat %>%
  group_by(depvar2) %>%
  summarise(n = n(),
            mean_coef = mean(coef, na.rm = T),
            median_coef = median(coef, na.rm = T)) %>%
  mutate(pct = round(n/sum(n, na.rm = T), digits = 2)) %>%
  select(depvar2, n, pct, mean_coef, median_coef)

kable(aux)

### Descriptive Stats of Moderators by Year

```{r, echo=F}

#TABLE 2 ABOUT HERE: Moderator, frequency, percentage (mean and median for publication year)

aux = dat %>%
  group_by(depvar2, year) %>%
  summarise(n = n(),
            mean_coef = round(mean(coef, na.rm = T), digits = 3),
            median_coef = round(median(coef, na.rm = T), digits = 3)) %>%
  group_by(year) %>%
  mutate(pct = paste0(100*(round(n/sum(n, na.rm = T), digits = 2)), " %")) %>%
  select(depvar2, year, n, pct, mean_coef, median_coef) %>%
  arrange(year) %>%
  rename(Moderator = depvar2,
         Year = year,
         N = n,
         Pct = pct,
         Mean = mean_coef,
         Median = median_coef
         )

kable(aux)

@@

f1 <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(aes(color = group)) +
  # Error Bars
  geom_errorbarh(aes(color = group), height = 0.1) +
  # Colors
  scale_color_manual(values = c("#000000", "#8b0000")) + 
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank(),
        legend.position = "none",
        axis.text.y = element_text(size = 15, hjust = 1.1),
        axis.text.x = element_text(size = 15, hjust = 1.1)) 
f1
```

```{r,include=F,warning=F}
f1 + 
  labs(caption = "ExpPC x N") +
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank(),
        legend.position = "none",
        axis.text.y = element_text(size = 18, hjust = 1.1),
        axis.text.x = element_text(size = 15, hjust = 1.1),
        plot.caption = element_text(size=22))

ggsave("./plots/fa.png", width = 30, height = 18.75, units = "cm")

@@

f1b <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(aes(color = group)) +
  # Error Bars
  geom_errorbarh(aes(color = group), height = 0.1) +
  # Colors
  scale_color_manual(values = c("#000000", "#8b0000")) + 
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank(),
        legend.position = "none",
        axis.text.y = element_text(size = 15, hjust = 1.1),
        axis.text.x = element_text(size = 15, hjust = 1.1))

@@

f2 <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(aes(color = group)) +
  # Error Bars
  geom_errorbarh(aes(color = group), height = 0.1) +
  # Colors
  scale_color_manual(values = c("#000000", "#8b0000")) + 
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank(),
        legend.position = "none",
        axis.text.y = element_text(size = 15, hjust = 1.1),
        axis.text.x = element_text(size = 15, hjust = 1.1)) 
f2
```

```{r,include=F,warning=F}
f2 + 
  labs(caption = "PCTGDP x N") +
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank(),
        legend.position = "none",
        axis.text.y = element_text(size = 18, hjust = 1.1),
        axis.text.x = element_text(size = 15, hjust = 1.1),
        plot.caption = element_text(size=22))

ggsave("./plots/fb.png", width = 30, height = 18.75, units = "cm")

@@

f3 <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(aes(color = group)) +
  # Error Bars
  geom_errorbarh(aes(color = group), height = 0.1) +
  # Colors
  scale_color_manual(values = c("#000000", "#8b0000")) + 
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank(),
        legend.position = "none",
        axis.text.y = element_text(size = 15, hjust = 1.1),
        axis.text.x = element_text(size = 15, hjust = 1.1))

f3
```

```{r,include=F,warning=F}
f3 + 
  labs(caption = "logExpPC x N") +
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank(),
        legend.position = "none",
        axis.text.y = element_text(size = 18, hjust = 1.1),
        axis.text.x = element_text(size = 15, hjust = 1.1),
        plot.caption = element_text(size=22))

ggsave("./plots/fc.png", width = 30, height = 18.75, units = "cm")

@@

f4 <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(aes(color = group)) +
  # Error Bars
  geom_errorbarh(aes(color = group), height = 0.1) +
  # Colors
  scale_color_manual(values = c("#000000", "#8b0000")) + 
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank(),
        legend.position = "none",
        axis.text.y = element_text(size = 15, hjust = 1.1),
        axis.text.x = element_text(size = 15, hjust = 1.1))

f4
```

```{r,include=F,warning=F}
f4 + 
  labs(caption = "PCTGDP x logN") +
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank(),
        legend.position = "none",
        axis.text.y = element_text(size = 18, hjust = 1.1),
        axis.text.x = element_text(size = 15, hjust = 1.1),
        plot.caption = element_text(size=22))

ggsave("./plots/fd.png", width = 30, height = 18.75, units = "cm")

@@

f5 <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(aes(color = group)) +
  # Error Bars
  geom_errorbarh(aes(color = group), height = 0.1) +
  # Colors
  scale_color_manual(values = c("#000000", "#8b0000")) + 
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank(),
        legend.position = "none",
        axis.text.y = element_text(size = 15, hjust = 1.1),
        axis.text.x = element_text(size = 15, hjust = 1.1))

f5
```

```{r,include=F,warning=F}
f5 + 
  labs(caption = "logExpPC x logN") +
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank(),
        legend.position = "none",
        axis.text.y = element_text(size = 18, hjust = 1.1),
        axis.text.x = element_text(size = 15, hjust = 1.1),
        plot.caption = element_text(size=22))

ggsave("./plots/fe.png", width = 30, height = 18.75, units = "cm")

@@

f6 <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(aes(color = group)) +
  # Error Bars
  geom_errorbarh(aes(color = group), height = 0.1) +
  # Colors
  scale_color_manual(values = c("#000000", "#8b0000")) + 
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank(),
        legend.position = "none",
        axis.text.y = element_text(size = 15, hjust = 1.1),
        axis.text.x = element_text(size = 15, hjust = 1.1))

f6
```

```{r,include=F,warning=F}
f6 + 
  labs(caption = "ExpPC x K") +
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank(),
        legend.position = "none",
        axis.text.y = element_text(size = 18, hjust = 1.1),
        axis.text.x = element_text(size = 15, hjust = 1.1),
        plot.caption = element_text(size=22))

ggsave("./plots/ff.png", width = 30, height = 18.75, units = "cm")

@@

f7 <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(aes(color = group)) +
  # Error Bars
  geom_errorbarh(aes(color = group), height = 0.1) +
  # Colors
  scale_color_manual(values = c("#000000", "#8b0000")) + 
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank(),
        legend.position = "none",
        axis.text.y = element_text(size = 15, hjust = 1.1),
        axis.text.x = element_text(size = 15, hjust = 1.1))

f7
```

```{r,include=F,warning=F}
f7 + 
  labs(caption = "PCTGDP x K") +
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank(),
        legend.position = "none",
        axis.text.y = element_text(size = 18, hjust = 1.1),
        axis.text.x = element_text(size = 15, hjust = 1.1),
        plot.caption = element_text(size=22))

ggsave("./plots/fg.png", width = 30, height = 18.75, units = "cm")

@@

```{r,include=F,warning=F}
blank = ggplot() + 
  geom_blank() +
  theme_minimal()
blank
ggsave("./plots/zz_blank.png", width = 30, height = 18.75, units = "cm")

plots = list.files(path = "./plots/", pattern = "*.png") %>%
  map(~{
    image_read(path = paste0("./plots/", .x)) %>%
      image_rotate(., 270) %>%
      image_border(., "#ffffff ", "90x18")
  })
```

```{r, echo=FALSE, fig.width=20, fig.height=5}

@@

```{r, echo=FALSE, fig.width=12, fig.height=6, fig.cap="Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)",warning=FALSE}
mod2 <- tibble(
  TE = mod$TE,
  seTE = mod$seTE,
  studlab = mod$studlab,
  lower = mod$lower,
  upper = mod$upper,
  group = "A") %>%
  bind_rows(.,
            aux = tibble(
              TE = c(mod$TE.random, NA),
              seTE = c(mod$seTE.random, NA),
              studlab = c("Overall Effect", "Prediction Interval"),
              lower = c(mod$lower.random, mod$lower.predict),
              upper = c(mod$upper.random, mod$upper.predict),
              group = "B")) %>%
  group_by(studlab) %>%
  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
  ungroup()

f8 <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(aes(color = group)) +
  # Error Bars
  geom_errorbarh(aes(color = group), height = 0.1) +
  # Colors
  scale_color_manual(values = c("#000000", "#8b0000")) + 
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank(),
        legend.position = "none",
        axis.text.y = element_text(size = 9, hjust = 1.1),
        axis.text.x = element_text(size = 15, hjust = 1.1))

f8
```

```{r,include=F,warning=F}
f8 + 
  labs(caption = "ExpPC x N") +
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank(),
        legend.position = "none",
        axis.text.y = element_text(size = 15, hjust = 1.1),
        axis.text.x = element_text(size = 15, hjust = 1.1),
        plot.caption = element_text(size=22))

ggsave("./plots/fh.png", width = 30, height = 18.75, units = "cm")

@@

f8b <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(aes(color = group)) +
  # Error Bars
  geom_errorbarh(aes(color = group), height = 0.1) +
  # Colors
  scale_color_manual(values = c("#000000", "#8b0000")) + 
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank(),
        legend.position = "none",
        axis.text.y = element_text(size = 13, hjust = 1.1),
        axis.text.x = element_text(size = 15, hjust = 1.1)) 
f8b
```

@@

f9 <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(aes(color = group)) +
  # Error Bars
  geom_errorbarh(aes(color = group), height = 0.1) +
  # Colors
  scale_color_manual(values = c("#000000", "#8b0000")) + 
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank(),
        legend.position = "none",
        axis.text.y = element_text(size = 10, hjust = 1.1),
        axis.text.x = element_text(size = 15, hjust = 1.1)) 
f9
```

```{r,include=F,warning=F}
f9 + 
  labs(caption = "PCTGDP x N") +
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank(),
        legend.position = "none",
        axis.text.y = element_text(size = 13, hjust = 1.1),
        axis.text.x = element_text(size = 15, hjust = 1.1),
        plot.caption = element_text(size=22))

ggsave("./plots/fi.png", width = 30, height = 18.75, units = "cm")

@@

f10 <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(aes(color = group)) +
  # Error Bars
  geom_errorbarh(aes(color = group), height = 0.1) +
  # Colors
  scale_color_manual(values = c("#000000", "#8b0000")) + 
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank(),
        legend.position = "none",
        axis.text.y = element_text(size = 13, hjust = 1.1),
        axis.text.x = element_text(size = 15, hjust = 1.1))

f10
```

```{r,include=F,warning=F}
f10 + 
  labs(caption = "logExpPC x N") +
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank(),
        legend.position = "none",
        axis.text.y = element_text(size = 15, hjust = 1.1),
        axis.text.x = element_text(size = 15, hjust = 1.1),
        plot.caption = element_text(size=22))

ggsave("./plots/fj.png", width = 30, height = 18.75, units = "cm")

@@

f11 <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(aes(color = group)) +
  # Error Bars
  geom_errorbarh(aes(color = group), height = 0.1) +
  # Colors
  scale_color_manual(values = c("#000000", "#8b0000")) + 
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank(),
        legend.position = "none",
        axis.text.y = element_text(size = 15, hjust = 1.1),
        axis.text.x = element_text(size = 15, hjust = 1.1))

f11
```

```{r,include=F,warning=F}
f11 + 
  labs(caption = "PCTGDP x logN") +
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank(),
        legend.position = "none",
        axis.text.y = element_text(size = 20, hjust = 1.1),
        axis.text.x = element_text(size = 15, hjust = 1.1),
        plot.caption = element_text(size=22))

ggsave("./plots/fk.png", width = 30, height = 18.75, units = "cm")

@@

```{r, echo=FALSE, fig.width=20, fig.height=2}

@@

### Meta-regressions for Expenditure measured as

@@

```{r, echo=FALSE}
mod = permutest(mod, progbar = F)
mod
